---
title: "RMarkdown and Leaflet"
author: "Sachin Sharma"
date: "10/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Peer-graded Assignment: R Markdown and Leaflet



<h1 style = "color:red">Scope of the assignment</h1>

<h2 style = "color:blue">Create a web page using R Markdown that features a map created with Leaflet.</h2>

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

```{r}

library(leaflet)

new_icon <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = "red"
)

content <- paste(sep = "<br/>",
  "<b>Data Science Zone</b>",
  "MG Road",
  "New Delhi, 110030"
)

my_map <- leaflet() %>%
    addTiles() %>%
    addAwesomeMarkers(lat = 28.4994, lng = 77.1622,
        icon = new_icon,
        popup = "R Programmer Expert") %>%
    addPopups(lat = 28.4994 , lng = 77.1622, content,
        options = popupOptions(closeButton = FALSE)
    )
my_map

```